Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-07 article.tex
Color changes for 8/12

Compilation refers to the process of translating from one language to another, most often from a high-level programming language intended for humans to work with, to machine- or bytecode intended to be executed on a target platform. This process can be divided into several distinct phases, which are grouped into one of two stages colloquially referred to as the \textit{frontend} and \textit{backend}. The former translating a high-level programming language to an \textit{intermediate representation} (IR) and the latter translating IR to executable machine code of a target architecture or bytecode of a target \textit{virtual machine} (VM).

@@

Continuous sequences of instructions are referred to as \textit{basic blocks}. A basic block is defined as a sequence of instructions with no branches in or out except for the first instruction, which follows immediately either the function entry point or a label,  and the last instruction, which either terminates or transfers the flow of execution, hence these are often referred to as terminators and can be thought of as a different categoriy of instructions entirely.

Basic blocks represent a single node in a \textit{control flow graph} (CFG), which is a directed graph whose edges denote transfer of  control flow. The unconditional branch terminator always transfers control flow to the block labelled, meaning only one successor will follow, whereas conditional branching could transfer to either of the two, but because control flow analysis is not concerned with data, it simply adds both as successors. % TODO: rets 
While each block has 0-2 immediate successors, the amount of predecessors is unbounded.

@@

The purpose of liveness analysis is to determine which variables are live at which program point, which in turn is used to

@@

Coalescing is the process of eliminating moves/copies of data from one GPR to another by combining their interference graph nodes.

@@

\newpage
\subsection{Benchmarking}

@@

\paragraph{fib.ll}
The 'dumb' fib is a very naive approach to finding the \(n\)th number of the Fibonacci sequence by calling itself recursively twice (decrementing \(n\) before each), which causes an exponential growth in function calls.
\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 fib & clang & greedy & simple & linear \\ [0.5ex] 
 \hline
 40 & 1.000000 & 1.438693 & 1.441270 & 0.73 \\ [1ex] 
 41 & 1.000000 & 1.441035 & 1.440626 & 0.73 \\ [1ex] 
 42 & 	1.000000 & 1.447140 & 1.446094 & 0\\
 \hline
\end{tabular}
\end{center}

>>>>

Compilation refers to the process of translating from one language to another, most often from a high-level programming language intended for humans to work with, to machine- or bytecode intended to be executed on a target platform. This process can be divided into several distinct phases, which are grouped into one of two stages colloquially referred to as the \textit{frontend} and \textit{backend}. \textcolor{orange}{The former translating a high-level programming language to an \textit{intermediate representation} (IR) and the latter translating IR to executable machine code of a target architecture or bytecode of a target \textit{virtual machine} (VM).}

@@

\textcolor{mygreen}{
Continuous sequences of instructions are referred to as \textit{basic blocks}. A basic block is defined as a sequence of instructions with no branches in or out except for the first instruction, which follows immediately either the function entry point or a label,  and the last instruction, which either terminates or transfers the flow of execution, hence these are often referred to as terminators and can be thought of as a different categoriy of instructions entirely.
}

\textcolor{mygreen}{
Basic blocks represent a single node in a \textit{control flow graph} (CFG), which is a directed graph whose edges denote transfer of  control flow. The unconditional branch terminator always transfers control flow to the block labelled, meaning only one successor will follow, whereas conditional branching could transfer to either of the two, but because control flow analysis is not concerned with data, it simply adds both as successors. % TODO: rets 
While each block has 0-2 immediate successors, the amount of predecessors is unbounded.
}

@@

\color{mygreen}
The purpose of liveness analysis is to determine which variables are live at which program point, which in turn is used to

@@

Coalescing is the process of eliminating moves/copies of data from one GPR to another by combining their interference graph nodes.
\color{black}

@@

\color{mygreen}
\subsection{Benchmarking}

@@

\paragraph{fib.ll}
The 'dumb' fib is a very naive approach to finding the \(n\)th number of the Fibonacci sequence by calling itself recursively twice (decrementing \(n\) before each), which causes an exponential growth in function calls.
\color{black}
\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 fib & clang & greedy & simple & linear \\ [0.5ex] 
 \hline
 40 & 1.000000 & 1.438693 & 1.441270 & 0.73 \\ [1ex] 
 41 & 1.000000 & 1.441035 & 1.440626 & 0.73 \\ [1ex] 
 42 & 	1.000000 & 1.447140 & 1.446094 & 0\\
 \hline
\end{tabular}
\end{center}
